Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Move LatGal and semi-additive category to after current section 2 intro.

An important observation about the semilattice homomorphisms that appear in adjoint pairs in $\LatGal$ is that
pointwise lifting of $\meet$ to meet-semilattice homomorphisms $f, g: X \to Y$, where $(f \meet g)(x) = f(x)
\meet g(x): X \to Y$, gives a notion of ``addition'' for these maps which is associative and commutative, and
which has a ``zero'' homomorphism $0_{X,Y}: X \to Y$ given by the constant map sending any $x \in X$ to $0_Y$,
acting as a unit for addition of homomorphisms. The same can be said for the join-preserving maps from $X$ to
$Y$, which also have a commutative monoid structure; Galois connections inherit this structure component-wise.
We now say more generally how this so-called \emph{semi-additive} structure on morphisms arises and explain
its significance to adapting CHAD to provide a semantic basis for Galois slicing as well as automatic
differentiation.

The product/coproduct is called a \emph{biproduct}, and the biproduct structure is denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. \todo{State biproduct ``laws''
that follow from this formulation.} A semi-additive category $\cat{C}$ is enriched in $\CMon$, the category of
commutative monoids: for any two morphisms $f, g: X \to Y$ in $\cat{C}$, the biproduct structure provides a
way to ``add'' them together, forming a morphism $f + g: X \to Y$. Diagrammatically:

@@

>>>>

@@

An important observation about the semilattice homomorphisms that appear in adjoint pairs in $\LatGal$ is that
the pointwise lifting of $\meet$ to meet-semilattice homomorphisms $f, g: X \to Y$, where $(f \meet g)(x) =
f(x) \meet g(x): X \to Y$, gives a notion of ``addition'' for those maps which is associative and commutative,
and which has a ``zero'' homomorphism $0_{X,Y}: X \to Y$ given by the constant map sending any $x \in X$ to
$0_Y$, acting as a unit for addition of homomorphisms. The same can be said for the join-preserving maps from
$Y$ to $X$, which also have a commutative monoid structure; Galois connections then inherit this structure
component-wise.

We now say more generally when this so-called \emph{semi-additive} structure on morphisms arises and explain
its role in generalising CHAD from automatic differentiation to providing a semantics for Galois slicing as
well.

The product/coproduct is called a \emph{biproduct}, and the biproduct structure is denoted by $(\biprod, 0)$.
The unit $0$ is both terminal and initial and is called a \emph{zero} object. \todo{State the biproduct
``laws'' that follow from this formulation.} A semi-additive category $\cat{C}$ is enriched in $\CMon$, the
category of commutative monoids: for any two morphisms $f, g: X \to Y$ in $\cat{C}$, the biproduct structure
provides a way to ``add'' them together, forming a morphism $f + g: X \to Y$. Diagrammatically:
